Model-based variable selection for regression with highly correlated variables.

### 2014-05-01 www/article13.tex
up ident
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/correg@563 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

We want to find the most probable structure $S$ knowing the dataset, so we search for the structure that maximizes $P(S|\boldsymbol{X})$ and we have:	
	\begin{eqnarray}
	 \label{approxBIC} P(S|\boldsymbol{X})&\propto & P(\boldsymbol{X}|S)P(S)
	=P(\boldsymbol{X}_r|\boldsymbol{X}_f,S)P(\boldsymbol{X}_f|S)P(S)
	\end{eqnarray}
So we will try to maximize $\psi(\boldsymbol{X},S)=P(\boldsymbol{X}|S)P(S)$.
	The discrete structure $S$ is identifiable under some hypothesis detailed in appendix, that is we can't permute some sub-regressions in (\ref{SR}) and obtain the same joint distribution $P(\boldsymbol{X},\boldsymbol{Y})$.

	\subsection{Modeling the uncorrelated covariates: a full generative approach on $P(\boldsymbol{X})$} \label{sectionfullgen}
	To be able to compare structures with $P(S|\boldsymbol{X})$, we need a full generative model on $\boldsymbol{X}$. Sub-regressions give $P(\boldsymbol{X}_r|\boldsymbol{X}_f,S) $ but $P(\boldsymbol{X}_f|S)$ is still undefined. We suppose that variables in $\boldsymbol{X}_f$ follow Gaussian mixtures of $k_j \in \mathbf{N}^*$ components: 
	\begin{equation}
			\forall \boldsymbol{X}^j \notin \boldsymbol{X}_r : \boldsymbol{X}^j_{|S} \sim f(\boldsymbol{\theta}_j)=\mathcal{GM}(\boldsymbol{\pi}_j;\boldsymbol{\mu}_j;\boldsymbol{\sigma}^2_j) \textrm{ with } \boldsymbol{\pi}_j,\boldsymbol{\mu}_j,\boldsymbol{\sigma}^2_j \textrm{ vectors of size } K_j. \label{mixtureX1}
		\end{equation}
		The great flexibility \cite{mclachlan2004finite} of such models makes our model more robust but one can use other laws if needed (exponentially distributed for example). Gaussian case is just a special case ($K_j=1$) of Gaussian mixture so it is included in our hypothesis but identifiability of $S$ requires to have at least one Gaussian mixture with at least two distinct components in each sub-regression (theorem and proof in appendix \ref{preuveident}). Identifiability if $S$ is not necessary to use a given structure but helps to find it.

		Variables in $\boldsymbol{X}_f$ are in the followings supposed to be independent.
	%Thus if one have some hypothesis on the distribution of some variables (exponentially distributed for example) it is possible to use it without impacting the model in other ways. %compute corresponding $\psi$ according to it. %and then improve the walk (will keep a structure only if it is really relevant).%and give it as an input of \textsc{CorReg} and then improve the efficiency of the algorithm (it will find a structure only if it is really relevant).
	We now have a full generative model.

@@

\section{Acknowledgements}
	We want to thanks ArcelorMittal Atlantique \& Lorraine that has granted this work, given the chance to use \textsc{CorReg} on real dataset and authorized the package to be open-sourced licensed (\textsc{CeCILL}), especially Dunkerque's site where most of the work has been done.
\bibliography{biblio}{}
\bibliographystyle{plain}
\section{Appendices}
	\subsection{Identifiability of the structure}
	The model presented above relies on a discrete structure $S$ between the covariates. But to find it we need identifiability property to insure the MCMC will asymptotically find the true model. Identifiability of the discrete structure is asked in following terms: Is it possible to find another structure $\tilde{S}$ of linear regression between the covariates leading to the same joint distribution and marginal distributions?

@@

	\subsubsection{Identifiability of $\Theta$}		
		We know by identifiability of the Gaussian mixtures and linear regression ($\boldsymbol{X}_f'\boldsymbol{X}_f$ is of full rank) that if $P(\boldsymbol{X}|S,\Theta)=P(\boldsymbol{X}|S,\tilde{\Theta})$ then $\Theta=\tilde{\Theta}$ up to a permutation of the components. But the identifiability of the discrete parameter $S$ is still pending.

	\subsubsection{Identifiability of $S$, quick look}

	In the following, $\otimes$ and $\oplus$ denote respectively the kronecker product and sum.
	\begin{eqnarray}
			\forall j \in I_r : \  \boldsymbol{X}^j_{|\boldsymbol{X}_f}&\sim & \mathcal{N}(\boldsymbol{X}_f\boldsymbol{\alpha}_j,\sigma^2_j\boldsymbol{I}_n) \label{densitycondgauche}\\
			\forall j \in I_f : \boldsymbol{X}^j_{|S} &\sim& \mathcal{GM}(\boldsymbol{\pi}_j;\boldsymbol{\mu}_j;\boldsymbol{\sigma}^2_j) \textrm{ with } \boldsymbol{\pi}_j,\boldsymbol{\mu}_j,\boldsymbol{\sigma}^2_j \textrm{ vectors of size } K_j  \label{densitydroite}\\
			\textrm{And we obtain, } \forall j \in I_r : \  \boldsymbol{X}^j&\sim & 
						\mathcal{GM}(\bigotimes_{\substack{i \in I_f^j  }}\boldsymbol{\pi}_i \ ; 
			                         \bigoplus_{\substack{i \in I_f^j  }} \alpha_{i,j} \boldsymbol{\mu}_i \ ; 
			                         \boldsymbol{\sigma}_j^2+\bigoplus_{\substack{i \in I_f^j  }}\alpha_{i,j}^2 \boldsymbol{\sigma}_i^2 )\label{densitygauche}          
		\end{eqnarray}
		So when we compare (\ref{densitydroite}) and (\ref{densitygauche}) we see that the number of components in $I_r$ variables differs when subregressions are of length $>1$ (almost 2 predictors) with multiple-class predictors (so the kronecker product is effective). We call this difference in component number "identifiability" in the sense that we try to find the model with the fewest component in $\boldsymbol{X}_f$ (we use the BIC so when comparing two models with the same likelihood, the one with fewer parameters will win). So in this case we have a "better" model (the simplest one) in the group of equivalent-meaning models (permuting variables in some sub-regression).
	\\

	\subsubsection{Identifiability: Theorem and proof} \label{preuveident}
		A necessary and sufficient condition for identifiability of $S$ is $\forall j \in I_r: K_j\geq 2$ with at least two distinct components in $(\boldsymbol{\mu}_j,\boldsymbol{\sigma}_j)$
\\
	{\it Proof}:
	We know that for a Gaussian multivariate distribution $(\boldsymbol{X}_r,\boldsymbol{X}_f)$ the conditional distributions $(\boldsymbol{X}_r|\boldsymbol{X}_f)$ and $(\boldsymbol{X}_f|\boldsymbol{X}_r)$ are both Gaussian (multivariate or not according to $p_r$).

		If $\exists j \in I_r: k_j=1$ (Gaussian) then all the covariates on the right of the associated sub-regression (with non-zero coefficients) are Gaussian and then the sub-regression can be permuted and is not identifiable. So if $\boldsymbol{X}^j$ are Gaussian mixtures, it is a necessary condition for identifiability to have $\forall j \in I_r: K_j\geq 2$ with at least two distinct components in $(\boldsymbol{\mu}_j,\boldsymbol{\sigma}_j)$.

	Gaussian mixtures in $\boldsymbol{X_r}$ with at least two distinct components does imply the presence of at least one Gaussian mixture in each sub-regression (with at least two components).
%	\begin{equation}
%	 \forall j \in I_f :    \boldsymbol{X}^j_{|S}=\sum_{k=1}^{K_j}\pi_j(k)\mathcal{N}\left(\mu_j(k),\sigma_j^2(k)\boldsymbol{I}_n\right) \\
%	\end{equation}
%	$\forall j \in I_r$ we can define $K_{j}$ the number of distinct components of $\boldsymbol{X}_j$.
%	\begin{eqnarray}
%				\boldsymbol{X}^{j}_{|S}&=&\sum_{k=1}^{K_j}\pi_j(k)\mathcal{N}\left(\mu_j(k),\sigma_j^2(k)\boldsymbol{I}_n\right)
%	\end{eqnarray}
	The joint distribution of the $p$ Gaussian mixtures is a multivariate Gaussian mixture $\boldsymbol{X}$ with $K\geq 2$ distinct components $(\boldsymbol{m}_k,\boldsymbol{\Sigma}_k)$ where $\boldsymbol{m}_k \in \mathbf{R}^p$ and $\boldsymbol{\Sigma}_k$ is a $p \times p$ matrix.
		We decompose the joint distribution based on the components:

		\begin{equation}
			f(\boldsymbol{X}_r,\boldsymbol{X}_f)= \sum_{k=1}^K p_kf(\boldsymbol{X}_r,\boldsymbol{X}_f|k)
	\end{equation}
			where  $\forall 1\leq k \leq K$, $ f(\boldsymbol{X}_r,\boldsymbol{X}_f|k)$  is a multivariate Gaussian.
			\\
			Then,  $\forall j \in I_r, \forall i \in I_f^j$ we have:
			\begin{equation}
			 f(\boldsymbol{X}_r,\boldsymbol{X}_f)= \sum_{k=1}^K p_kf(\boldsymbol{X}^i|\boldsymbol{X}_r,\boldsymbol{X}_f\setminus\boldsymbol{X}^i,k)f(\boldsymbol{X}_r,\boldsymbol{X}_f\setminus\boldsymbol{X}^i|k)
	\end{equation}
				where the $f(\boldsymbol{X}^i|\boldsymbol{X}_r,\boldsymbol{X}_f\setminus\boldsymbol{X}^i,k)$ are Gaussian.

Hence,
\begin{equation}
				f(\boldsymbol{X}^i|\boldsymbol{X}\setminus\boldsymbol{X}^i)=f(\boldsymbol{X}^i|\boldsymbol{X}_r,\boldsymbol{X}_f\setminus\boldsymbol{X}^i)=\sum_{k=1}^Kp_kf(\boldsymbol{X}^i|\boldsymbol{X}_r,\boldsymbol{X}_f\setminus\boldsymbol{X}^i,k)
				\end{equation}

				is a Gaussian mixture.

%				Identifiability of $S$ means we don't have a linear regression of $\boldsymbol{X}^i$ on $(\boldsymbol{X}_r,\boldsymbol{X}_f\setminus\boldsymbol{X}^i)$. So we need a non-linear relationship or a not-Gaussian residual $f(\boldsymbol{X}^i|\boldsymbol{X}_r,\boldsymbol{X}\setminus\boldsymbol{X}^i)$, {\it i.e. } the Gaussian mixture $f(\boldsymbol{X}^i|\boldsymbol{X}\setminus\boldsymbol{X}^i)$ should have at least two distinct components.
%	Linear relationship means $\exists \boldsymbol{\gamma} \in \mathbf{R}^{p-1}$ and $\sigma_i \in \mathbf{R}$ for which
%	\begin{equation}
%		\forall 1\leq k \leq K, \boldsymbol{X}^i_{|\boldsymbol{X}_r,\boldsymbol{X}\setminus\boldsymbol{X}^i,k}=\mathcal{N}(\boldsymbol{m}_k^{\bar{i}}\boldsymbol{\gamma},\sigma_i^2)
%	\end{equation}
%					
%				
%				\begin{equation}
%				f(\boldsymbol{X}^i|\boldsymbol{X}\setminus\boldsymbol{X}^i)=f(\boldsymbol{X}^i|\boldsymbol{X}_r,\boldsymbol{X}_f\setminus\boldsymbol{X}^i)=\sum_{k=1}^Kp_kf(\boldsymbol{X}^i|\boldsymbol{X}_r,\boldsymbol{X}_f\setminus\boldsymbol{X}^i,k)
%				\end{equation}
%				
				If it is a Gaussian mixture with at least two distinct components when $\boldsymbol{X}^j \in \boldsymbol{X}_r$ has at least two distinct components.
				Then $\boldsymbol{X}^i$ can't be explained by a linear regression on the other covariates (non-Gaussian residual).		
				 So we have identifiability of the structure $S$ even for trivial sub-regressions if we keep the constraint to have distinct components in $\boldsymbol{X}_r$ (equivalent to have at least one Gaussian mixture with at least two components in each sub-regression).
%			%f(\boldsymbol{X}_r,\boldsymbol{X}_f)&=& sum_{j=1}^K 
%
%The distribution of $\boldsymbol{X}_r$ is a Gaussian mixture defined in (\ref{densitygauche}) thus
%			$\forall 1\leq k \leq K$,  $(\boldsymbol{X}_r|k)$ is Gaussian: 
%		
%
%
%In the followings, $N_{11}$ and $N_{12}$ Gaussian (multivariate or not). $\boldsymbol{X}_r$ is here supposed to be univariate (identifiability in such a case will be generalisable).
%		\begin{eqnarray}
%			f(\boldsymbol{X_f})&=& p_{11} N_{11}+p_{12}N_{12}\\
%			\boldsymbol{X}_r&=&\boldsymbol{X}_f\boldsymbol{\alpha}_r +\boldsymbol{\varepsilon}_r \\
%			f(\boldsymbol{X}_r)&=&p_{11}(N_{11}+\boldsymbol{\varepsilon})+p_{12}(N_{12}+\boldsymbol{\varepsilon}) \\
%			f(\boldsymbol{X}_r|\boldsymbol{X}_f)&=&\boldsymbol{\varepsilon}\\
%			f(\boldsymbol{X}_r,\boldsymbol{X}_f)&=&f(\boldsymbol{X}_r|\boldsymbol{X}_f)f(\boldsymbol{X}_f)=f(\boldsymbol{X}_f|\boldsymbol{X}_r)f(\boldsymbol{X}_r) \\
%			f(\boldsymbol{X}_f|\boldsymbol{X}_r)&=&\frac{f(\boldsymbol{X}_r|\boldsymbol{X}_f)f(\boldsymbol{X}_f)}{f(\boldsymbol{X}_r)} \\
%			&=&\frac{(p_{11} N_{11}+p_{12}N_{12})\boldsymbol{\varepsilon}}{p_{11}(N_{11}+\boldsymbol{\varepsilon})+p_{12}(N_{12}+\boldsymbol{\varepsilon})} \textrm{ with }p_{11}+p_{12}=1\\
%			&=&\frac{(p_{11} N_{11}+p_{12}N_{12})\boldsymbol{\varepsilon}}{(p_{11} N_{11}+p_{12}N_{12})+\boldsymbol{\varepsilon}}
%		\end{eqnarray}
%	So we have a quotient of two multivariate Gaussian mixtures and the question is to know if it is Gaussian (in such a case we wouldn't have identifiability).
%If $\boldsymbol{X}_f$ is a Gaussian mixture with $K>1$ distinct components, then so will be $\boldsymbol{X}_r$.
%	
%	If the sufficient condition is not satisfied but we have different variances for $\boldsymbol{X}_f$ and $\boldsymbol{X}_r$, then we don't have identifiability but reverse regressions don't give the same results as the true model, as illustrated in the well-known salary discrimination study \cite{goldberger1984reverse} and explained in books and papers (\cite{leamer1978least},\cite{cameron2005microeconometrics}).
%

>>>>

We want to find the most probable structure $S$ knowing the dataset, so we search for the structure that maximizes $P(S|\boldsymbol{X})$ and we have:	
	\begin{eqnarray}
	 \label{approxBIC} P(S|\boldsymbol{X})&\propto & P(\boldsymbol{X}|S)P(S)
	=P(\boldsymbol{X}_r|\boldsymbol{X}_f,S)P(\boldsymbol{X}_f|S)P(S)
	\end{eqnarray}
So we will try to maximize $\psi(\boldsymbol{X},S)=P(\boldsymbol{X}|S)P(S)$.

	\subsection{Modeling the uncorrelated covariates: a full generative approach on $P(\boldsymbol{X})$} \label{sectionfullgen}
	To be able to compare structures with $P(S|\boldsymbol{X})$, we need a full generative model on $\boldsymbol{X}$. Sub-regressions give $P(\boldsymbol{X}_r|\boldsymbol{X}_f,S) $ but $P(\boldsymbol{X}_f|S)$ is still undefined. We suppose that variables in $\boldsymbol{X}_f$ follow Gaussian mixtures of $k_j \in \mathbf{N}^*$ components: 
	\begin{equation}
			\forall \boldsymbol{X}^j \notin \boldsymbol{X}_r : \boldsymbol{X}^j_{|S} \sim f(\boldsymbol{\theta}_j)=\mathcal{GM}(\boldsymbol{\pi}_j;\boldsymbol{\mu}_j;\boldsymbol{\sigma}^2_j) \textrm{ with } \boldsymbol{\pi}_j,\boldsymbol{\mu}_j,\boldsymbol{\sigma}^2_j \textrm{ vectors of size } K_j. \label{mixtureX1}
		\end{equation}
		The great flexibility \cite{mclachlan2004finite} of such models makes our model more robust. Gaussian case is just a special case ($K_j=1$) of Gaussian mixture so it is included in our hypothesis but identifiability of $S$ requires to have at least one Gaussian mixture with at least two distinct components in each sub-regression (derived from the identifiability of the SR model in \cite{maugis2009variable}, more details in the Appendices \ref{preuveident}).

		Remark:  Identifiability if $S$ is not necessary to use a given structure but helps to find it.

		Variables in $\boldsymbol{X}_f$ are in the followings supposed to be independent Gaussian mixtures with at least two distinct components each.
	%Thus if one have some hypothesis on the distribution of some variables (exponentially distributed for example) it is possible to use it without impacting the model in other ways. %compute corresponding $\psi$ according to it. %and then improve the walk (will keep a structure only if it is really relevant).%and give it as an input of \textsc{CorReg} and then improve the efficiency of the algorithm (it will find a structure only if it is really relevant).
	We now have a full generative model.

@@

\section{Acknowledgements}
	We want to thanks ArcelorMittal Atlantique \& Lorraine that has granted this work, given the chance to use \textsc{CorReg} on real dataset and authorized the package to be open-sourced licensed (\textsc{CeCILL}), especially Dunkerque's site where most of the work has been done.
\bibliography{biblio}{}
\bibliographystyle{plain}
\section{Appendices}
	\subsection{Identifiability of the structure} \label{preuveident}
	The model presented above relies on a discrete structure $S$ between the covariates. But to find it we need identifiability property to insure the MCMC will asymptotically find the true model. Identifiability of the structure is asked in following terms: Is it possible to find another structure $\tilde{S}$ of linear regression between the covariates leading to the same joint distribution and marginal distributions?

@@

%	\subsubsection{Identifiability of $\Theta$}		
%		We know by identifiability of the Gaussian mixtures and linear regression ($\boldsymbol{X}_f'\boldsymbol{X}_f$ is of full rank) that if $P(\boldsymbol{X}|S,\Theta)=P(\boldsymbol{X}|S,\tilde{\Theta})$ then $\Theta=\tilde{\Theta}$ up to a permutation of the components. But the identifiability of the discrete parameter $S$ is still pending.
%		
%	\subsubsection{Identifiability of $S$, quick look}
%	
%	In the following, $\otimes$ and $\oplus$ denote respectively the kronecker product and sum.
%	\begin{eqnarray}
%			\forall j \in I_r : \  \boldsymbol{X}^j_{|\boldsymbol{X}_f}&\sim & \mathcal{N}(\boldsymbol{X}_f\boldsymbol{\alpha}_j,\sigma^2_j\boldsymbol{I}_n) \label{densitycondgauche}\\
%			\forall j \in I_f : \boldsymbol{X}^j_{|S} &\sim& \mathcal{GM}(\boldsymbol{\pi}_j;\boldsymbol{\mu}_j;\boldsymbol{\sigma}^2_j) \textrm{ with } \boldsymbol{\pi}_j,\boldsymbol{\mu}_j,\boldsymbol{\sigma}^2_j \textrm{ vectors of size } K_j  \label{densitydroite}\\
%			\textrm{And we obtain, } \forall j \in I_r : \  \boldsymbol{X}^j&\sim & 
%						\mathcal{GM}(\bigotimes_{\substack{i \in I_f^j  }}\boldsymbol{\pi}_i \ ; 
%			                         \bigoplus_{\substack{i \in I_f^j  }} \alpha_{i,j} \boldsymbol{\mu}_i \ ; 
%			                         \boldsymbol{\sigma}_j^2+\bigoplus_{\substack{i \in I_f^j  }}\alpha_{i,j}^2 \boldsymbol{\sigma}_i^2 )\label{densitygauche}          
%		\end{eqnarray}
%		So when we compare (\ref{densitydroite}) and (\ref{densitygauche}) we see that the number of components in $I_r$ variables differs when subregressions are of length $>1$ (almost 2 predictors) with multiple-class predictors (so the kronecker product is effective). We call this difference in component number "identifiability" in the sense that we try to find the model with the fewest component in $\boldsymbol{X}_f$ (we use the BIC so when comparing two models with the same likelihood, the one with fewer parameters will win). So in this case we have a "better" model (the simplest one) in the group of equivalent-meaning models (permuting variables in some sub-regression).
%	\\
%	
If all the variables in $\boldsymbol{X}$ are Gaussian mixtures with at least two distinct components, then the model of sub-regression is identifiable (from the identifiability of the SR model by Maugis \cite{maugis2009variable}).

But making this hypothesis on $\boldsymbol{X}_r$ is sufficient.
In the followings, we call Gaussian mixture the Gaussian mixtures with at least two distinct components, and Gaussian mixtures with equal components are called Gaussian (in fact they are).

First, we observe that if each variable in $\boldsymbol{X}_r$ is a Gaussian mixture, then there is at least one Gaussian mixture on the right of each sub-regression. So there is a non-empty subset of $\boldsymbol{X} \subset \boldsymbol{X}_f$ containing Gaussian mixtures. We note $\boldsymbol{X}_{S^c}$ its complement (empty or not) in $\boldsymbol{X}_f$

The theorem from Maugis guarantee that a sub-regression between Gaussian mixtures is identifiable.
		For each sub-regression, 
%	\subsubsection{Identifiability: Theorem and proof} 
%		A necessary and sufficient condition for identifiability of $S$ is $\forall j \in I_r: K_j\geq 2$ with at least two distinct components in $(\boldsymbol{\mu}_j,\boldsymbol{\sigma}_j)$
%\\
%	{\it Proof}:
%	We know that for a Gaussian multivariate distribution $(\boldsymbol{X}_r,\boldsymbol{X}_f)$ the conditional distributions $(\boldsymbol{X}_r|\boldsymbol{X}_f)$ and $(\boldsymbol{X}_f|\boldsymbol{X}_r)$ are both Gaussian (multivariate or not according to $p_r$). 
%	
%		If $\exists j \in I_r: k_j=1$ (Gaussian) then all the covariates on the right of the associated sub-regression (with non-zero coefficients) are Gaussian and then the sub-regression can be permuted and is not identifiable. So if $\boldsymbol{X}^j$ are Gaussian mixtures, it is a necessary condition for identifiability to have $\forall j \in I_r: K_j\geq 2$ with at least two distinct components in $(\boldsymbol{\mu}_j,\boldsymbol{\sigma}_j)$.
%
%	Gaussian mixtures in $\boldsymbol{X_r}$ with at least two distinct components does imply the presence of at least one Gaussian mixture in each sub-regression (with at least two components).
%%	\begin{equation}
%%	 \forall j \in I_f :    \boldsymbol{X}^j_{|S}=\sum_{k=1}^{K_j}\pi_j(k)\mathcal{N}\left(\mu_j(k),\sigma_j^2(k)\boldsymbol{I}_n\right) \\
%%	\end{equation}
%%	$\forall j \in I_r$ we can define $K_{j}$ the number of distinct components of $\boldsymbol{X}_j$.
%%	\begin{eqnarray}
%%				\boldsymbol{X}^{j}_{|S}&=&\sum_{k=1}^{K_j}\pi_j(k)\mathcal{N}\left(\mu_j(k),\sigma_j^2(k)\boldsymbol{I}_n\right)
%%	\end{eqnarray}
%	The joint distribution of the $p$ Gaussian mixtures is a multivariate Gaussian mixture $\boldsymbol{X}$ with $K\geq 2$ distinct components $(\boldsymbol{m}_k,\boldsymbol{\Sigma}_k)$ where $\boldsymbol{m}_k \in \mathbf{R}^p$ and $\boldsymbol{\Sigma}_k$ is a $p \times p$ matrix.
%		We decompose the joint distribution based on the components:
%		
%		\begin{equation}
%			f(\boldsymbol{X}_r,\boldsymbol{X}_f)= \sum_{k=1}^K p_kf(\boldsymbol{X}_r,\boldsymbol{X}_f|k)
%	\end{equation}
%			where  $\forall 1\leq k \leq K$, $ f(\boldsymbol{X}_r,\boldsymbol{X}_f|k)$  is a multivariate Gaussian.
%			\\
%			Then,  $\forall j \in I_r, \forall i \in I_f^j$ we have:
%			\begin{equation}
%			 f(\boldsymbol{X}_r,\boldsymbol{X}_f)= \sum_{k=1}^K p_kf(\boldsymbol{X}^i|\boldsymbol{X}_r,\boldsymbol{X}_f\setminus\boldsymbol{X}^i,k)f(\boldsymbol{X}_r,\boldsymbol{X}_f\setminus\boldsymbol{X}^i|k)
%	\end{equation}
%				where the $f(\boldsymbol{X}^i|\boldsymbol{X}_r,\boldsymbol{X}_f\setminus\boldsymbol{X}^i,k)$ are Gaussian.
%				
%Hence,
%\begin{equation}
%				f(\boldsymbol{X}^i|\boldsymbol{X}\setminus\boldsymbol{X}^i)=f(\boldsymbol{X}^i|\boldsymbol{X}_r,\boldsymbol{X}_f\setminus\boldsymbol{X}^i)=\sum_{k=1}^Kp_kf(\boldsymbol{X}^i|\boldsymbol{X}_r,\boldsymbol{X}_f\setminus\boldsymbol{X}^i,k)
%				\end{equation}
%				
%				is a Gaussian mixture.				
%				
%				Identifiability of $S$ means we don't have a linear regression of $\boldsymbol{X}^i$ on $(\boldsymbol{X}_r,\boldsymbol{X}_f\setminus\boldsymbol{X}^i)$. So we need a non-linear relationship or a not-Gaussian residual $f(\boldsymbol{X}^i|\boldsymbol{X}_r,\boldsymbol{X}\setminus\boldsymbol{X}^i)$, {\it i.e. } the Gaussian mixture $f(\boldsymbol{X}^i|\boldsymbol{X}\setminus\boldsymbol{X}^i)$ should have at least two distinct components.
%	Linear relationship means $\exists \boldsymbol{\gamma} \in \mathbf{R}^{p-1}$ and $\sigma_i \in \mathbf{R}$ for which
%	\begin{equation}
%		\forall 1\leq k \leq K, \boldsymbol{X}^i_{|\boldsymbol{X}_r,\boldsymbol{X}\setminus\boldsymbol{X}^i,k}=\mathcal{N}(\boldsymbol{m}_k^{\bar{i}}\boldsymbol{\gamma},\sigma_i^2)
%	\end{equation}
%					
%				
%				\begin{equation}
%				f(\boldsymbol{X}^i|\boldsymbol{X}\setminus\boldsymbol{X}^i)=f(\boldsymbol{X}^i|\boldsymbol{X}_r,\boldsymbol{X}_f\setminus\boldsymbol{X}^i)=\sum_{k=1}^Kp_kf(\boldsymbol{X}^i|\boldsymbol{X}_r,\boldsymbol{X}_f\setminus\boldsymbol{X}^i,k)
%				\end{equation}
%				
%				If it is a Gaussian mixture with at least two distinct components when $\boldsymbol{X}^j \in \boldsymbol{X}_r$ has at least two distinct components.
%				Then $\boldsymbol{X}^i$ can't be explained by a linear regression on the other covariates (non-Gaussian residual).		
%				 So we have identifiability of the structure $S$ even for trivial sub-regressions if we keep the constraint to have distinct components in $\boldsymbol{X}_r$ (equivalent to have at least one Gaussian mixture with at least two components in each sub-regression).
%			%f(\boldsymbol{X}_r,\boldsymbol{X}_f)&=& sum_{j=1}^K 
%
%The distribution of $\boldsymbol{X}_r$ is a Gaussian mixture defined in (\ref{densitygauche}) thus
%			$\forall 1\leq k \leq K$,  $(\boldsymbol{X}_r|k)$ is Gaussian: 
%		
%
%
%In the followings, $N_{11}$ and $N_{12}$ Gaussian (multivariate or not). $\boldsymbol{X}_r$ is here supposed to be univariate (identifiability in such a case will be generalisable).
%		\begin{eqnarray}
%			f(\boldsymbol{X_f})&=& p_{11} N_{11}+p_{12}N_{12}\\
%			\boldsymbol{X}_r&=&\boldsymbol{X}_f\boldsymbol{\alpha}_r +\boldsymbol{\varepsilon}_r \\
%			f(\boldsymbol{X}_r)&=&p_{11}(N_{11}+\boldsymbol{\varepsilon})+p_{12}(N_{12}+\boldsymbol{\varepsilon}) \\
%			f(\boldsymbol{X}_r|\boldsymbol{X}_f)&=&\boldsymbol{\varepsilon}\\
%			f(\boldsymbol{X}_r,\boldsymbol{X}_f)&=&f(\boldsymbol{X}_r|\boldsymbol{X}_f)f(\boldsymbol{X}_f)=f(\boldsymbol{X}_f|\boldsymbol{X}_r)f(\boldsymbol{X}_r) \\
%			f(\boldsymbol{X}_f|\boldsymbol{X}_r)&=&\frac{f(\boldsymbol{X}_r|\boldsymbol{X}_f)f(\boldsymbol{X}_f)}{f(\boldsymbol{X}_r)} \\
%			&=&\frac{(p_{11} N_{11}+p_{12}N_{12})\boldsymbol{\varepsilon}}{p_{11}(N_{11}+\boldsymbol{\varepsilon})+p_{12}(N_{12}+\boldsymbol{\varepsilon})} \textrm{ with }p_{11}+p_{12}=1\\
%			&=&\frac{(p_{11} N_{11}+p_{12}N_{12})\boldsymbol{\varepsilon}}{(p_{11} N_{11}+p_{12}N_{12})+\boldsymbol{\varepsilon}}
%		\end{eqnarray}
%	So we have a quotient of two multivariate Gaussian mixtures and the question is to know if it is Gaussian (in such a case we wouldn't have identifiability).
%If $\boldsymbol{X}_f$ is a Gaussian mixture with $K>1$ distinct components, then so will be $\boldsymbol{X}_r$.
%	
%	If the sufficient condition is not satisfied but we have different variances for $\boldsymbol{X}_f$ and $\boldsymbol{X}_r$, then we don't have identifiability but reverse regressions don't give the same results as the true model, as illustrated in the well-known salary discrimination study \cite{goldberger1984reverse} and explained in books and papers (\cite{leamer1978least},\cite{cameron2005microeconometrics}).
%
